Correlating Scanning Ion Conductance and Super-Resolved Fluorescence Microscopy

### 2020-09-30 sections/correlated-sicm-and-srfm.tex
Update correlated-sicm-and-srfm.tex

Beside the different topographies of these two cells, they also display different types of actin 
fibres. In the inside of the first mentioned round cell nearly no actin signal could be detected 
(some dot-like structures were marked with purple arrowheads), whereas at the borders of the cell 
some hair-like structures were visible (white arrow). The long, flat cell showed some long actin 
fibres (yellow arrowheads).

>>>>

Beside the different topographies of these two cells, they also display different types of actin 
fibres. In the inside of the first mentioned round cell nearly no actin signal could be detected 
(some dot-like structures were marked with purple arrowheads), whereas at the borders of the cell 
some hair-like structures were visible (white arrow). The long, flat cell showed some long actin 
fibres (yellow arrowheads). The cell marked with the white arrow, that was ending with a white 
dot, could be just seen half in the confocal/STED images and dot-like actin structures 
predominate.

Structures that would have been missed by using one single technique alone: 
\textsf{
\begin{tabular}[c]{p{6cm}|p{3cm}|p{3.75cm}}
\label{tab:missing_structures}
What? & visible in fig.~\ref{fig:SICM_STED1} by SICM & visible in fig.~\ref{fig:SICM_STED1} by STED microscopy \\ \hline
The full extend of the protrusion & YES & \textbf{NO} \\ \hline
The connection between the roundish and the flat cell & \textbf{NO} & YES \\
\end{tabular}}
